Dark matter halo shape in the Auriga simulations: radial dependence, time evolution and baryon disk alignment

### 2019-07-17 Document/paper.tex
edit

\subsection{Correlation with baryonic disk properties}

From our characterization of radial shapes it is clear that
MHD halos are rounder than DM halos every sampled radii. 
It is also noticeable that the rounding effect of baryons is stronger
at the disk regime, where the DM halo is almost perfectly oblate. 
Furthermore, MHD halos tend towards more oblate shapes (T < 0.5)
despite DM halos tendency towards more prolate shapes (T>0.5). 
This rounding effect can be explained by gravitational effect of the
flattened axisymmetric galactic disk. 
It also explanes the weakness of this affect around $\approx 100$kpc,
where the disk potential is weaker compared to the DM halo potential.

@@

In this paper we measured the shape of thirty isolated Milky Way like 
dark matter haloes simulated in the Auriga project using the zoom-in
technique. 
Six of these haloes are also simulated at higher resolution.
The simulations

>>>>

In this paper we measured the shape of thirty isolated Milky Way like 
dark matter haloes simulated in the Auriga project using the zoom-in
technique. 
We also used six of these haloes that were simulated at higher
resolution. 
The Auriga project simulated these halos with two different setups:
dark matter only (DMO) simulation and full magnetohydrodynamics (MHD)
includeing star formation and feedback.
We used the shape measurement algorithm by \cite{Allgood06} on the
dark matter halos of these two kinds of simulations.

We find that MHD halos are rounder than DMO halos every sampled radii. 
MHD halos tend towards more oblate shapes (T < 0.5)
despite DM halos tendency towards more prolate shapes (T>0.5). 
It is also noticeable that the rounding effect of baryons is stronger
at the disk regime, where the haloes are close to oblate.

This rounding effect can be explained by gravitational effect of the
flattened axisymmetric galactic disk. 
It also explanes the weakness of this affect around $\approx 100$kpc,
where the disk potential is weaker compared to the DM halo potential.

@@
